Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-29 paper/paper.tex
fix pingscan plusible rules

    \midrule
    Black Nurse & - & - & - & - \\    
    Ping Scan & 6 & 5 & 2\Mar{18?} & 1 \\
    SYN Flood & 4 & 2 & 2 & 2 \\
    UDP Teardrop & - & - & - & - \\
    UDP Flood & - & - & - & - \\
    \midrule
    Apache Struts 2 & - & - & - & - \\
    ColdFusion & 7 & 19 & 34 & 1\\
    iisadmin access & 4 & 17 & \Fix{861} & \Fix{1} \\        
    JBoss JMX & 5 & 23 & 228 & 5 \\
    Script tag in URI & 23 & 22 & 786 & 1 \\
    WeBid & 1 & 23 & - & -\\    
    Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 984 & 2\\
    .idq access & 14 & 19 & 511 & 1 \\
    /system32/ in URI & 4 & 20 & 1,913 & 1 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

    \midrule
    Black Nurse & - & - & - & - \\    
    Ping Scan & 6 & 5 & 9 & 1 \\
    SYN Flood & 4 & 2 & 2 & 2 \\
    UDP Teardrop & - & - & - & - \\
    UDP Flood & - & - & - & - \\
    \midrule
    Apache Struts 2 & - & - & - & - \\
    ColdFusion & 7 & 19 & 34 & 1\\
    iisadmin access & 4 & 17 & \Fix{861} & \Fix{1} \\        
    JBoss JMX & 5 & 23 & 228 & 5 \\
    Script tag in URI & 23 & 22 & 786 & 1 \\
    WeBid & 1 & 23 & - & -\\    
    Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 984 & 2\\
    .idq access & 14 & 19 & 511 & 1 \\
    /system32/ in URI & 4 & 20 & 1,913 & 1 \\
    \bottomrule
  \end{tabular}
\end{table}
